---
title: "R Notebook"
output: html_notebook
---


```{r setup, Libraries, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

# Document Creation
library(knitr)
library(markdown)
library(yaml)
library(distill)
library(blogdown)

# Basic Analysis
library(ggplot2)
library(tidyverse)
library(clipr)
library(dbplyr)
library(data.table)
library(stringr)
library(stringi)
library(tibble)
library(tidyr)

# SNA - Social Network Analysis

library(tergm)
library(ergm)
library(network)
library(networkDynamic)
library(networkDynamicData)

library(statnet)
library(igraph)
library(igraphdata)
library(tsna)
library(sna)

```

```{r Set Working Directory, include=FALSE}
getwd()

setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments")

```


## Basic R: Import & Clean Data

```{r Read raw data into R}

library(readr)

indx_SmugglerCove_recip <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv", 
    col_names = FALSE, 
    col_types = cols(X1 = col_skip(),
                     X4 = col_skip()), 
                    na = "empty")

# View(indx_SmugglerCove_recip)
summary(indx_SmugglerCove_recip)

 # Smuggler's Cove

smugCovIdx <- indx_SmugglerCove_recip

```

```{r Getting Information on a Dataset:, echo=FALSE}

# list the structure of smugCovIdx
str(smugCovIdx)

# class of an object (numeric, matrix, data frame, etc)
class(smugCovIdx)

# list the variables in smugCovIdx
names(smugCovIdx)

# dimensions of an object
dim(smugCovIdx)
```

```{r & Clean Data}

  library(stringr)
      # Drop NA rows
smugCovIdx <- na.omit(smugCovIdx) 

# DATA Cleaning


#     Extract variables
#####

          # extract first word of the column, adds values in new Column at the end of DF

                    #1st pastIt
passIt <- smugCovIdx      

colnames(passIt)
                    #2nd passIt
passIt$substring_first <- 
  str_extract(passIt$X5,"(\\w+)") 

colnames(passIt)
#####

#####
#     Drop it like...
#####
      # DROP COLUMNS FROM DATA FRAME
                      
                      #3rd PassIt
passIt = subset(passIt, 
                       select = -c(3,4)
                       )
colnames(passIt)
#####

#####
#     Give Variables a human name
#####

# rename column names with human language

                      # Return it
smugCovIdx <- passIt

names(smugCovIdx )[1] <- "dnkName"
names(smugCovIdx )[2] <- "dnkIng"
names(smugCovIdx )[3] <- "ingType"

colnames(smugCovIdx)
```

# Network: Creating network Data
```{r NETWORK: Network Formation}
passIt <- smugCovIdx
dim(passIt)
  #####
        #### Edgelist: Network Formation
            ## NOTE: Edgelist Format
#####
            ## network data is nx2 (or more with edge attributes)
            ## first column is "From", 
            ## second column is "To"
  #####
          ### Edgelist: inspect column names
              ## inspect column names as 3rd-kth columns of network_data may include network attributes

colnames(passIt)

```

```{r EDGELIST: IGRAPH: create a network object from the dataset, echo=TRUE}

 smug_unrIg <- smugCovIdx


smug_unrIg <-
  graph.data.frame(
    smug_unrIg[,1:3],
    directed = F)


summary(smug_unrIg)

##### Summary Output
#####
      # IGRAPH c6de075 UN-- 274 672 -- 
      # + attr: name (v/c), ingType (e/c)


```

```{r Edgelist: Statnet Network Object}

#Lets read the data into the enviroment.
#This will import it formatted as an edgelist

source_netEdge <- smugCovIdx

# Identify Edge Vertices and Edge Attributes

colnames(source_netEdge)
# dnkName <- "dnkName" 
# dnkIng <- "dnkIng"  
# edgeAT <- "ingType"



#Lets create an statnet object from our edgelist
#First we make the object. It will have no vertex or edge attributes
sourceEL_sn <- 
  network(as.matrix(source_netEdge[1:2], 
                    matrix.type = 'edgelist')
  )

#**%e%** Let's add edge atributes, do not include the colNames for edge vertex


sourceEL_sn%e%"ingType" <- source_netEdge$ingType
sourceEL_sn%e%"dnkIng" <- source_netEdge$dnkIng


# Generating the EdgeList

##**round 1**
          # from "_netEdge" select "colNames" to be identified with "vertex.names"

temp <- source_netEdge[,c("dnkName")]



##**round 2**
            # code still selecting from "_netEdge", add "colNames"

colnames(temp)<- c("dnkIng")


##**round 3**
            # "rBind" selects "colnames" from "_netEdge" and BINDS them to temp

temp<- rbind(temp, source_netEdge[, c("dnkIng")])



##**final round** !!! is being used as variable in generating an edgelist object
                # temp contains 
        

sourceEL_sn%v%"dnkName"<- 
  temp$dnkIng[match(sourceEL_sn%v%"vertex.names",
                    temp$dnkIng)]

print(sourceEL_sn)

# it's a bloody statnet edgelist 
```


# Network Info
## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}
#### dimensions of an object
dim()

#### class of an object
class()

# list the structure of smugCovIdx
str()

# class of an object (numeric, matrix, data frame, etc)
class()

# list the variables in smugCovIdx
names()

colnames( )

summary( )


```



## Directed Adjacency Matrix: Create & Describe

iGraph and Statnet both use {r graph4} for
Directed Adjacency Matrix Objects

```{r graph4, statnet: Directed: Adjacency Network, echo=TRUE}

    smugCovIdx.stat<-
        network(
        smugCovIdx,
        directed=F,
        matrix.type="adjacency"
        )

#     provides a description of several critical network features
    print(flo.stat)
    
```

```{r graph4, igraph: Directed: Adjacency Network, echo=TRUE}

    flo.ig<-
      graph.adjacency(
      flo,
      mode="undirected"
      ) 
    print(flo.ig)
```

```{r igraph: Network Description, echo=TRUE}

#     Count Vertices
    vcount(flo.ig)

#     Count Edges
    ecount(flo.ig)

# Is this a Bipartite or single mode network?
    is_bipartite(flo.ig)

#  Are edges directed or undirected?
    is_directed(flo.ig)

#Are edges weighted or unweighted?
    is_weighted(flo.ig)        
    
```




**Vertex and Edge Attributes**

```{r statnet: Attribute Data: Directed: Adjacency Network, echo=TRUE}

#     access vertex attributes
  head(flo.stat %v% "vertex.names")

#      list the names of vertex attributes
  network::list.vertex.attributes(flo.stat)

#     access edge attribute
  head(flo.stat%e% "weight")

#  Generate a list the names of edge attributes
  network::list.edge.attributes(flo.stat)
 
#   summarize numeric network attribute
  summary(flo.stat  %v% "name")
  
```

```{r igraph: Attribute Data: Directed: Adjacency Network, echo=TRUE}

#     access vertex attribute 
  V(flo.ig)$name
#     Generate a list the names of vertex attributes
  igraph::vertex_attr_names(flo.ig)

#     access edge attribute
  E(flo.ig)$weight

#   Generate a list the names of edge attributes  
  igraph::edge_attr_names(flo.ig)

#   summarize numeric network attribute
  summary(E(flo.ig)$weight)  

```



#   Week 2: Scripts
##    Network: Describe Network Data
##    *Identify and describe content of nodes and
    links,*


##    *Identify format of data set (i.e., matrix or
    edgelist, directed or not, weighted or not),
    and*

Vertex attribute names: vertex.names

```{r Network Attributes, echo=TRUE}

  network(smugCovIdx)

```

3.  *Identify whether attribute data are present.*

```{r Summary,echo=TRUE}
  
  summary(smugCovIdx,
          print.adj = TRUE
          )
```

#       Explore the dataset using commands from week 2 tutorial.

5.  *geodesic and path distances,*

## Path Length and Geodesic

```{r iGraph:Nodes: Path: Length, echo=TRUE}

#     Calculate distances between two nodes
    distances(flo.ig,"Bischeri","Ridolfi")

#     Calculate distance between two nodes using unweighted edges
    distances(flo.ig,"Bischeri", "Castellani",weights=NA)
    
```

We can also find all of the shortest paths between
two famalies in this network. These list the
starting node and the ending node with all nodes
inbetween for each path. The option weights=NA
means that any available edge weights are ignored.

```{r iGraph:Nodes: Path: Shortest, echo=TRUE}
    
#     isolating the distances between specific node
    all_shortest_paths(flo.ig,"Strozzi","Tornabuoni", weights=NA)$res
## Note: manually tell igraph to ignore edge weights.
```

The concept of shortest path to describe the
overall network structure can be more useful

```{r iGraph:Network: Path: Shortest, echo=TRUE}

#     find average shortest path for network
    average.path.length(flo.ig,directed=F)    
  
```

6.  *triads or transitivity,*

## Dyad Census

Classifies all dyads in the network as: -
Reciprocal (mutual), or mut - Asymmetric
(non-mutual), or asym, and - Absent, or null

```{r statnet: Dyad Census , echo=TRUE}

    sna::dyad.census(flo.stat)

```

```{r iGraph: Dyad Census, echo=TRUE}

  igraph::dyad.census(flo.ig)

```

## Triad Census

Classifies all triads in the network. The triad
census provides a fundamental descriptive insight
into the types of triads found in a particular
dataset.

```{r statnet: Triad Census, echo=TRUE}

#     Classify all Triad in the network: Directed Network
  sna::triad.census(flo.stat, mode= )

#     Classify all Triad in the network: Undirected Network
   sna::triad.census(flo.stat, mode="graph")

#     total number of all four triad types returned by triad census
   sum(sna::triad.census(flo.stat, mode="graph"))
   
   
```

```{r iGraph: Triad Census, echo=TRUE}
#Classify all Triad in the network
     igraph::triad_census(flo.ig)

```

## Transitivity or Global Clustering

```{r iGraph: weighted/ network transitivity, echo=TRUE}

#     network transitivity:
    transitivity(flo.ig)

#     weighted network transitivity:
#   igraph::transivity(flo.ig)

```

```{r statnet: weighted/ directed network transitivity, echo=TRUE}

#     Directed Networks transitivity:
  gtrans(flo.stat)

#   methods for weighted networks, rank and correlation, along with the relevant references.
#  sna::gtrans()
  
```

## Local Transivity or Clustering

`Local transitivity` (local clustering
coefficient), is a technical description of the
density of an ego network.

```{r iGraph:Local transitivity, echo=TRUE}

#     Retrive a list of the vertices we are interested
    V(flo.ig)[c("Bischeri" ,
                "Castellani", 
                "Medici",
                "Ridolfi")]

#     check ego network transitivity
transitivity(flo.ig,
             type="local", 
             vids=V(flo.ig)
             [c("Bischeri",
                "Castellani", 
                "Medici",
                "Ridolfi")]) 
#     get global clustering cofficient
  transitivity(flo.ig, type="global")

#     get average local clustering coefficient
  transitivity(flo.ig, type="average")

```

7.  *connectedness and.or component structure,
    etc.*

> Distill is a publication format for scientific
> and technical writing, native to the web.
>
> Learn more about using Distill for R Markdown at
> <https://rstudio.github.io/distill>. ##
