---
title: "R Notebook"
output: html_notebook
---
 
# $vertex.names is NA because dnkNam and dnkType were fed into the "To" column


          
```{r EDGELIST: UNDIRECTED Network Objects: statnet & igraph, eval=FALSE, include=FALSE}

#Lets make some network objects

colnames(smugCovIdx) 
# tell R data should be understood as a matrix
smugEL_mx = as.matrix(smugCovIdx[c(4,3)],
                        matrix.type="edgelist",
                        directed=T) 
  View(smugEL_mx)
  class(smugEL_mx)
  summary(smugEL_mx)
  
  # dnkIng             ingTyp         
 #  Length:672         Length:672      

network_edgelist <- smugEL_mx
  class(network_edgelist)
  summary(network_edgelist)

        ### View(network_nodes)
    
######
      ######**igraph** 
######
        #igraph object 
network_ig <-
    graph.edgelist(network_edgelist, 
    directed=T)

  summary(network_ig)
  class(network_ig)
  View(network_ig)
  
                ## create new edge attribute
  E(network_ig)$dnkNam<-smugCovIdx$dnkNam
  E(network_ig)$ingNam<-smugCovIdx$ingNam
  V(network_ig)$ingType <- smugCovIdx$ingType
  
  #create vertex attributes in igraph
 
summary(network_ig)

  # head(network_ig)
  # summary(network_ig)
      ######
 
#####
      #####**statnet** 
#####    
  network_edgelist <- smugCovIdx
 
  network_nodes <- smugCovIdx 
  network_nodes<- 
    select(network_nodes,
           dnkNam)
summary(network_nodes)
View(network_nodes)

  #Now let's create a statnet object
  network_statnet <- network(smugEL_mx, 
                             matrix.type = "edgelist",
                             multiple = T)
  
  network_statnet%e%"dnkIng" <- network_edgelist$dnkIng
  
  network_statnet%e%'ingTyp'<- 
    network_edgelist$ingTyp

       # list the names: vertex attributes
  view(network_statnet%v% "vertex.names")
  
summary()
 network::list.vertex.attributes(network_statnet)
  summary(network_statnet%v%"dnkNam")
  print(network_statnet)
        #####

 ## Network Objects: EDGE LIST
              ##**STATNET:**
  smugEL_sn <- network_statnet
  
                ##**IGRAPH:** 
  smugEL_ig <- network_ig
  
```

          
```{r EDGELIST: IGRAPH: DIRECTED Network: ingTyp, include=FALSE}

#Lets make some network objects

colnames(smugCovIdx) 


#####
# tell R data should be understood as a matrix
smugEL_mx = as.matrix(smugCovIdx[(3:4)],
                        matrix.type="edgelist",
                        directed=T) 
head.matrix(smugEL_mx)
view(summary(smugEL_mx))

networkEL_mx <- smugEL_mx


        ### View(nodes_ingTyp)
    
######
      ######**igraph** 
######
        #igraph object: ingTyp
d_network_ig <- graph.edgelist(networkEL_mx, 
                               directed = T)
  summary(d_network_ig)    

 #              [1] "dnkNam" "ingNam" "dnkIng" "ingTyp"
     ## create new edge attribute
  E(d_network_ig)$dnkIng<-smugCovIdx$ingNam
  E(d_network_ig)$dnkNam<-smugCovIdx$dnkNam
    
  #create vertex attributes in igraph
 V(d_network_ig)[match(V(d_network_ig)$ingTyp,nodes_ingTyp$ingTyp)]$ingTyp<- nodes_ingTyp$ingTyp

 V(d_network_ig)[match(V(d_network_ig)$ingTyp,nodes_ingTyp$ingTyp)]$ingTyp<- nodes_ingTyp$ingTyp
 ver
  
 vertex_attr_names()
 
   View(d_network_ig)
   head(d_network_ig)
  summary(d_network_ig)
edge_attr(d_network_ig)
  summary(vertex.attributes(d_network_ig))
    
   ingTypEL_Dig <- d_network_ig
```


# Meta Data: smugEL_ig
Name: smugEL-ig
Type: List [10](s3: igraph)
Value: List Length 10

**List Class**
[1] 
smugEL_ig[[1]]
    Type: Double [1]
    Value: 274
[2] 
smugEL_ig[[2]]
    Type: Logical [1]
    Value: False

    *?* Adjacency List *?*
[3]
smugEL_ig[[3]]
    Type: double [672]
    Value: 1 2 3 ... 273 237 273
[4]
smugEL_ig[[4]]
    Type:  double [672]
    Value: 0 0 0 ... 18 13 37
[5]
smugEL_ig[[5]]
    Type:  double [672]
    Value: 0 1 2  ... 664 665 671
[6]
smugEL_ig[[6]]
    Type:  double [672]
    Value: 0 1 2  ... 617 630 636
[7]
smugEL_ig[[7]]
    Type:  double [275]
    Value: 0 0 1 ... 655 661 672
[8]
smugEL_ig[[8]]
    Type:  double [275]
    Value: 0 6 7 ... 672 672 672

[9]
smugEL_ig[[9]]
    Type: List [4]
    Value: 
  
  [[9]][[1]]
      Type: Double [3]
      Value: 1 0 1
  
  [[9]][[2]]     
      Type: List [0]
      Value: named list()

**[[9]][[3]]**
      name: Name
          Type: charachter [274]
          Value: "drink names"
      name: Dnk Name
          Type: charachter [274]
          **Value: NA**

  [[9]][[4]]       
        Name: dnkIng
            Type: Character [672]
            Value:  "Drink Ingredients"
        Name: ingType
            Type: Character [672]
            Value: "Ingredient Types"

[10]
smugEL_ig[[10]]
        Type: environment [3]
        Value: <environment: 0x000001f362d1cad8>

  [[10]][[".__igraph_version__."]]
            Type: character [1]
            Value: '0.8.0'

  [[10]][["me"]]    
        Replica of Name: smugEL-ig [1:10] with corresponding sub-sets

  [[10]][["myid"]]       
        Type: character [1]
        Value: "8d6f6c3c-903b-11ec-9ddd-db50f5a64f06"
        
        

```{r}


```




# Meta Data: smugEL_sn
View(smugEL_sn)

smugEL_sn 
        Type: list [5] (s3: network)
        Value: List Lenth 5

[["mel"]]
        Type: list[6720]
        Value: list length 672
      
      [["mel"]][[1]]
$inl
[1] 115
$outl
[1] 1

$atl
$atl$ingType
[1] "FRUIT"

$atl$na
[1] FALSE

$atl$dnkIng
[1] "(1-INCH-SQUARE) CHUNKS PINEAPPLE"        
        
        
      [["mel"]][[511]]
$inl
[1] 126

$outl
[1] 91

$atl
$atl$ingType
[1] "BITTERS"

$atl$na
[1] FALSE

$atl$dnkIng
[1] "ANGOSTURA BITTERS"
        


[["gal"]]        
        Type: list[7]
        Value: list length 7

    smugEL_sn[["gal"]]
$n
[1] 274

$mnext
[1] 673

$directed
[1] TRUE

$hyper
[1] FALSE

$loops
[1] FALSE

$multiple
[1] TRUE

$bipartite
[1] FALSE


[["val"]]
        Type: list[274]
        Value: list length274

  [["val"]][[1]]
      Name: NA
        Type: logical[1]
        Value: False
      Name: vertex.names
        Type: character [1]
        Value: List Lenth 3
      Name: dnkNames
        Type: character [1]
        Value: List Lenth 3

**[["iel"]]**
        Type: List [274]
        Value: List Length 274

    [["iel"]][[1:114]]
    **integer(0)**


**[["oel"]]**
       Type: List [274]
        Value: List Length 274

    [["oel"]][[115:274]]
    **integer(0)**



