
#: Visualization: ggplot2
```{r Visualization: ggplot2}

# Dependencies
 library(network)
 library(sna)
 library(ggplot2)
 
library(visNetwork)
library(threejs)
 library(networkD3)
 library(ndtv)
 # ggnetwork - This package allows to pass network objects to ggplot2 and provides geometries to plot their elements.
 
 library(ggnetwork)
 
  # visualize your network graphs 
 library(GGally)

## [network visualization with ggplot2]




```

# graph the SMUG network 

smug_attributes <- smugCovIdx
smug_edj <- smugCovIdx[2:3]
View(smug_edj)
#V1: dnkIng
#V2: ingTyp

smugNet <- 
  graph.edgelist(as.matrix(smug_edj), directed = T)

V(smugNet)$dnkIng <- 
  smug_attributes$dnkIng[match(V(smugNet)$name, smug_attributes$ingTyp)]

V(smugNet)$dnkNam <- 
  smug_attributes$dnkNam[
    match(V(
      smugNet)$name,
      smug_attributes$dnkIng)
    ]
summary(smugNet)

###**PLOT** in .R Doc

# IGRAPH

```{r igraph:}

library(igraph)



```

## Plotting: network data

### Plot Name: smugIG_plot-R_blue-curved-small\*

```{r igraph:plot: basic R }

library(igraph)
plot(smugEL_ig, 
     vertex.size=3,
     vertex.color = "blue",
     vertex.frame.color = NA,
     vertex.label = NA,
     edge.curved = 1.7,
     edge.arrow.size = .3, 
     edge.width = .5)


```

### **Plot: Kamada Kawai**

**Plot Name** igraph_kamadaLayout_smug

```{r igraph: Plot: Kamada Kawai}

library(igraph)

 # run the layout function on our graph
 
 kamadaLayout <-
   layout.kamada.kawai(smugEL_ig)
 
# change the default layout setting to equal the layout we generated above
 plot(smugEL_ig, 
      layout = kamadaLayout, 
      vertex.size = 3, 
      vertex.color = "black", 
      vertex.frame.color = NA, 
      vertex.label.cex = .7,  
      vertex.label = NA, 
      edge.curved = .3, 
      edge.arrow.size = .1, 
      edge.width = .5)
```

### **Plot: Frucherman-Reingold**

**Plot Name** igrap-smugEL_Frucherman-Reingold

```{r igraph:}

library(igraph)
 
# run the layout function on our graph
 fruchtermanLayout <- 
   layout.fruchterman.reingold(smugEL_ig)
 
 # and then we change the default layout setting to equal the layout we generated above
 
 plot(smugNet, 
      vertex.size = 6, 
      vertex.color= "orange",
      vertex.label.cex = .5, 
      vertex.label.color = "black", 
      edge.with = .5,
      edge.curved = 5,
      edge.arrow.size = 0.1)

```

## Plotting: attribute data

### **Plot: Color & Attribute**

**Plot Name: \$Vertex Naame and \$color**

```{r igraph:}

library(igraph)
 V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "PUKA PUNCH", "red", "yellow")
  V(smugEL_ig)$color <- NA
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "RUMBUSTION PUNCH", "red","yellow")
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "TRIUMVIRATE PUNCH", "red", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "KAHIKO PUNCH", "red", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == , "black", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name ==  "DOCTOR FUNK" , "green",V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name ==  "AKU AKU", "green",V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name ==  "JET PILOT" , "green",V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "SINGAPORE SLING", "purple", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name ==  "SCORPION", "purple", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "MAI TAI", "purple", V(smugEL_ig)$color)
  V(smugEL_ig)$color <- ifelse(V(smugEL_ig)$name == "MEXICAN EL DIABLO", "black", V(smugEL_ig)$color)
  
 
      plot(smugEL_ig, 
           vertex.size = 3, 
           vertex.frame.color =  "black", 
           vertex.label.cex = .7, 
           vertex.label = NA, 
           edge.curved = .5, 
           edge.arrow.size = .3)


```

```{r igraph:}

library(igraph)



```

# Statnet

```{r STATNET:}

library(statnet)
library(sna)




```

## Plotting: network data

```{r PLOT: Find strong components}
library(statnet)
library(sna)
cd <- component.dist(
  snEL,
  connected="strong")
cd$membership              #Who's in what component?
cd$csize                   #What are the component sizes?
                           #Plot the size distribution
plot(1:length(cd$cdist),
     cd$cdist/sum(cd$cdist),
     ylim=c(0,1),
     type="h")

lgc<- #Get largest component
  component.largest(snEL,
                    connected="strong")  

#Plot g, with component membership
gplot(snEL,
      vertex.col=2+lgc)  
      
#Plot largest component itself 
gplot(component.largest(
  snEL,
  connected="strong",
  result="graph"))


```

```{r STATNET: PLOT: Find weak components}

library(statnet)
library(sna)
cd<-component.dist(snEL,connected="weak")
cd$membership              #Who's in what component?
cd$csize                   #What are the component sizes?
                           #Plot the size distribution
plot(1:length(cd$cdist),cd$cdist/sum(cd$cdist),ylim=c(0,1),type="h")  
lgc<-component.largest(snEL,connected="weak")  #Get largest component
gplot(snEL,vertex.col=2+lgc)  #Plot g, with component membership
                           #Plot largest component itself 
gplot(component.largest(snEL,connected="weak",result="graph"))
```

```{r}

```

## Plotting: attribute data

## Plotting: Path Length and Geodesic Distance

```{r STATNET:Path: Geodesic number & lengths}
library(statnet)
library(sna)

gplot(geodist(snEL, 
        inf.replace=Inf, 
        count.paths=TRUE, 
        predecessors=FALSE,
        ignore.eval=FALSE, 
        na.omit=FALSE)
        )
```
